A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Add paragraphs to Results section.

\section*{Performance}
\subsection*{Baselines}
In addition to the $ContentBasedRecommender$ and the $NeighborhoodRecommender$,
we constructed and tested several other baseline algorithms to compare the
$LatentFeatureRecommender$ against. These baselines show that the performance of
$LatentFeatureRecommender$ is not due to a single mechanism but rather is the
result of the mult-stage algorithm. In this section, we briefly outline these
additional baselines.

@@

\subsection*{Results}

\begin{table}
\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$Random$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$Popularity$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMap$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModel$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBased$ & .014 & .020 & .016 &
\textbf{.115} & \textbf{.186} & \textbf{.142} \\ \hline 
$Neighborhood$ & .040 & .060 & .048 &
\textbf{.137} & \textbf{.240} & \textbf{.175} \\ \hline 
$LatentFeature$ & .036 & .060 & .045 &
\textbf{.174} & \textbf{.228} & \textbf{.197} \\ \hline
\end{tabular}
\caption{The performance of each of the recommenders across all categories. The
first five are the baseline recommenders outlined in the previous section. The
final three are the recommenders of interest, described in the Recommender
Algorithms section. The scores in bold are the most important results and are 
further illustrated in the following figure.}
\end{center}
\end{table}
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.65\textwidth]{RecommenderPerformance2.png}
	\caption{The performance of the three main recommenders in terms of
    2-metrics across all categories. We emphasize the 2-F1 Score as our most
    important single metric of comparison. We see that the $LatentFeatureRecommender$
    outperforms the other recommenders in this score.} 
    \label{fig:RecommenderPerformance} 
\end{figure}

Table (1) shows the results of all inter-catalogue recommenders across all
categories. For example, the {\em precision} column lists the sum, across all
categories, of correctly predicted edges divided by the sum, across all
categories, of predicted edges. We first point out that both $Neighborhood$ and
$LatentFeature$ outperform $ContentBased$ by all metrics. This makes clear the
utility of leveraging information from the recommendation when making
inter-catalogue recommendations. Next, we notice that $Neighborhood$ actually
outperforms $LatentFeature$ in {\em precision} by 10\% and in {\em 2-recall} by
about 5\%. Importantly, however, $LatentFeature$ bests $Neighborhood$ in the key
metric {\em 2-}$F_1$ by about 12\%.

\pagebreak
\section*{Conclusion}
In this study, we address the problem of determining inter-retailer, or
inter-catalogue, item-item associations. We frame this problem as a recommender
problem, which motivates a relatively straightforward experiment in which a
candidate algorithm must connect two recommendation graphs by guessing edges
between them.

>>>>

\pagebreak
\section*{Performance}
\subsection*{Baselines}
In addition to the $ContentBasedRecommender$ and the $NeighborhoodRecommender$,
we constructed and tested several other baseline algorithms to compare the
$LatentFeatureRecommender$ against. These baselines show that the performance of
$LatentFeatureRecommender$ is not due to a single mechanism but rather is the
result of the mult-stage algorithm. In this section, we briefly outline these
additional baselines.

@@

\pagebreak
\subsection*{Results}
Table (1) shows the results of all inter-catalogue recommenders across all
categories. For example, the {\em precision} column lists the sum, across all
categories, of correctly predicted edges divided by the sum, across all
categories, of predicted edges. We first point out that both $Neighborhood$ and
$LatentFeature$ outperform $ContentBased$ by all metrics. This makes clear the
utility of leveraging information from the recommendation when making
inter-catalogue recommendations. Next, we notice that $Neighborhood$ actually
outperforms $LatentFeature$ in {\em precision} by 10\% and in {\em 2-recall} by
about 5\%. Importantly, however, $LatentFeature$ bests $Neighborhood$ in the key
metric {\em 2-}$F_1$ by about 12\%.

Of course, $Random$ does quite poorly. Interestingly, $Popularity$ and
$RandomMap$ have comparable performance and score almost half as well as
$LatentFeature$. The fact that their results are similar is not suprising,
however, since they are both relying entirely on item popularity $\rho$.
$Popularity$ utilizes $\rho$ explicity by connecting each item to one of the
most popular items in the other catalogue. $RandomMap$, on the otherhand,
employs $\rho$ in an identical manner to that by $LatentFeature$. This reveals
that popularity alone accounts for nearly half of $LatentFeature$'s success.

\begin{table}
\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$Random$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$Popularity$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMap$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModel$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBased$ & .014 & .020 & .016 &
\textbf{.115} & \textbf{.186} & \textbf{.142} \\ \hline 
$Neighborhood$ & .040 & .060 & .048 &
\textbf{.137} & \textbf{.240} & \textbf{.175} \\ \hline 
$LatentFeature$ & .036 & .060 & .045 &
\textbf{.174} & \textbf{.228} & \textbf{.197} \\ \hline
\end{tabular}
\caption{The performance of each of the recommenders across all categories. The
first five are the baseline recommenders outlined in the previous section. The
final three are the recommenders of interest, described in the Recommender
Algorithms section. The scores in bold are the most important results and are 
further illustrated in the following figure.}
\end{center}
\end{table}
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.75\textwidth]{RecommenderPerformance2.png}
	\caption{The performance of the three main recommenders in terms of
    2-metrics across all categories. We emphasize the 2-F1 Score as our most
    important single metric of comparison. We see that the $LatentFeatureRecommender$
    outperforms the other recommenders in this score.} 
    \label{fig:RecommenderPerformance} 
\end{figure}

As expected, we find that $OneModel$ outperforms $LatentFeature$. Indeed, one
might ask why $OneModel$ does not score even higher. The performance of
$OneModel$ is limited by the rank reduction stage of the algorithm, which
discards a large amount of information. $LatentFeature$ benefits from this stage
since by discarding dimensions, the subsequent mapping problem becomes more
tractable. Nonetheless, it is interesting that $OneModel$ outperforms
$LatentFeature$ by a about a factor of 2. Given that $OneModel$ is a cheat that
involves perfectly mapped concept spaces, we can consider it a loose upperbound
for $LatentFeature$ (at least when working with 16 dimensions). It might,
therefore, be possible to signficantly improve the performance of
$LatentFeature$ by improving its concept space mapping stage.  At the same time,
it is not at all clear that such a mapping in general even exists. Rather, the
common existence of an approximate mapping is a hypothesis of the authors that
is corroborated by our experimental results for the present dataset.

\section*{Conclusion}
In this study, we address the problem of determining inter-retailer, or
inter-catalogue, item-item associations. We frame this problem as a recommender
problem, which motivates a relatively straightforward experiment in which a
candidate algorithm must connect two recommendation graphs by guessing edges
between them.
